Preliminary Draft

### 2021-07-21 article/draft.tex
add the data mining part and change a bit the last part of the intro

\begin{table}[]
\centering
\begin{tabular}{|l|c|l|l|l}

\hline
&  \begin{tabular}[c]{@{}l@{}} Application Programming Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}} Web Scraping \end{tabular}}                                                                                                                                                                 \\ \hline
 \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle API} and  \href{https://buzzsumo.com}{Buzzsumo API}   \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}    
\\ \hline
 \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet tw scrape}}                                                                                                                                                                           \\ \hline
 \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{YouTube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
\end{tabular}
\caption{Data collection}
\label{tab1}
\end{table}

Nevertheless, misinformation specific interventions by mainstream platforms are hard to monitor, study or verify by third parties (e.g. academic community, data journalists, NGOs), as in many cases misleading or false content does not qualify as a violation of a given platform's rules and it does not explicitly appear as a separate category in available transparency reports. This makes the study of online misinformation, the assessment of the impact of platforms' actions to tackle misinformation and their relevancy a burdensome task for the academic community. Hence, in the present article we explain how to verify with data mining mainstream platforms' current actions regarding content with low credibility or false information. We do so by providing a series of examples for different interventions and platforms. We only focus on three platforms: Facebook, Twitter and YouTube. Both Facebook and YouTube are in the top three most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}. More specifically, we survey a number of common policies used in order to tackle misinformation, across the three above cited mainstream platforms, Facebook, Twitter and YouTube: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices. We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies. We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring. For a detailed list of interventions of multiple platforms we invite the reader to check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.

@@

 We summarize in table \ref{tab1} the tools used to collect the data from Facebook, Twitter and YouTube, that we use in multiple examples throughout the present article. We compile in Appendix \ref{links} in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and YouTube that we discuss throughout the article. Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.  %the announced policy for a specific user was implemented or not.

>>>>

Nevertheless, misinformation specific interventions by mainstream platforms are hard to monitor, study or verify by third parties (e.g. academic community, data journalists, NGOs), as in many cases misleading or false content does not qualify as a violation of a given platform's rules and it does not explicitly appear as a separate category in available transparency reports. This makes the study of online misinformation, the assessment of the impact of platforms' actions to tackle misinformation and their relevancy a burdensome task for the academic community. Hence, in the present article we explain how to verify with data mining mainstream platforms' current actions regarding content with low credibility or false information. We do so by providing a series of examples for different interventions and platforms. We chose to focus on three platforms: Facebook, Twitter and YouTube. Both Facebook and YouTube are in the top three most popular social media platforms in terms of number of users.\footnote{See for example the ranking of the most popular social networks as of April 2021 on Statista: \href{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}{https://www.statista.com/statistics/272014/global-social-networks-ranked-by-number-of-users/}.} We further choose Twitter because it is a social networking platform with the most news-focused users, according to the Pew Research center (2019)~\cite{pew1}. To collect data from these three platforms, we either used the APIs (Application Programming Interfaces), or web scraping (i.e. retro-engineering the HMTL code of a web page to extract meaningful data, see Table \ref{tab1} for a summary). Minet, a webmining tool developed by the médialab \cite{minet}, was often used, and we scripted our own data mining code when it was necessary.

\begin{table}[h]
\centering
\begin{tabular}{|l|c|l|l|l}

\hline
&  \begin{tabular}[c]{@{}l@{}} Application Programming Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}} Web Scraping \end{tabular}}                                                                                                                                                                 \\ \hline
 \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle API} and  \href{https://buzzsumo.com}{Buzzsumo API}   \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{Code created for this article}    
\\ \hline
 \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet tw scrape}}                                                                                                                                                                           \\ \hline
 \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{YouTube API V3}      &                                                                                                                            \multicolumn{1}{l|}{Code created for this article}                                                                                                                                                                           \\ \hline
\end{tabular}
\caption{Data collection}
\label{tab1}
\end{table}

@@

In this article, we survey a number of common policies against misinformation used by Facebook, Twitter and YouTube, that we seperated in three broad categories: temporary or permanent suspension of users, reducing the visibility of some content, introducing flags and notices. Finally, we discuss how an increased effort of transparency regarding specific content can help the community of researchers study and assess the impact of platforms' policies regarding misinformation.

We do not provide  an exhaustive list of methods on how to investigate the platforms’ policies. We rather provide a methodology to investigate key policies, that can be useful to researchers or journalists interested in implementing external monitoring. For a detailed list of interventions of multiple platforms we invite the reader to check the following \href{https://airtable.com/shrO0ooI9WSEfIUhb/tblAWQwFOiihKdQjm/viwZLAOzLK1NQ0c2n?blocks=hide}{airtable} compiled by Slatz and Leibowicz (2021)~\cite{niemanlab}.

We compile in Appendix \ref{links} in table \ref{summary}, a list of links that redirect to the policies, regulations and transparency centers of Facebook, Twitter and YouTube that we discuss throughout the article.  %the announced policy for a specific user was implemented or not.
